The globular cluster system of the Auriga simulations

### 2019-09-05 AurigaGCS.tex
Time to submit to MNRAS

% Abstract of the paper
\begin{abstract}
We investigate whether the galaxy and star formation model used for the Auriga
simulations can produce a realistic GC population. We compare statistics of GC 
candidate star particles in the Auriga haloes with catalogues of the Milky Way 
(MW) and Andromeda (M31) GC populations. We find that the Auriga simulations do 
produce sufficient stellar mass for GC candidates at radii and metallicities that 
are typical for the MW GC system (GCS). We do observe varying mass-ratios of the
simulated GC candidates relative to the observed mass in the MW and M31 GC systems
for different bins of galactocentric radius-metallicity ($r_{\text{gal}}$-[Fe/H]).
This implies that different values for the combined product of the bound cluster 
formation efficiency and the GC disruption rate are needed. Overall, the Auriga 
simulations produce GC candidates with higher metallicities than the MW and M31 
GCS and they are found at larger radii than observed. Bound cluster formation
efficiencies higher than ten percent are needed for the metal-poor GC candidates,
and those within the Solar radius should experience negligible destruction rates.
GC candidates in the outer halo, on the other hand, should either have low formation
efficiencies, or experience high mass loss for the Auriga simulations to produce a
GCS that is consistent with that of the MW or M31. Finally, the scatter in the 
metallicity as well as in the radial distribution between different Auriga runs 
is considerably smaller than the differences between that of the MW and M31 GCSs. 
The Auriga model is unlikely to give rise to a GCS that can be consistent with
both galaxies.
\end{abstract}

@@

This model was tailored to the \textsc{arepo} code and calibrated to reproduce
key observables of galaxies, such as the history of the cosmic star formation rate
density, the stellar mass to halo mass relation, and galaxy luminosity functions.
The galaxy formation model produces realistic spiral galaxies at redshift $z=0$.
Moreover, Auriga reproduces the HI disc properties \citep{2017MNRAS.466.3859M},
the chemical thin/thick disc \citep{2018MNRAS.474.3629G}, the diversity in 
accreted stellar halo properties found in observations \citep{2019MNRAS.485.2589M},
and the \textit{Gaia} Sausage \citep{2019MNRAS.484.4471F}. These last two 
bolster the point that the simulations are similar (and detailed) enough to the 
MW to reproduce major, distinct features of the Galaxy, and so looking for the 
GC population properties and comparing them to the MW/M31 is all the more relevant.

@@

To ease this comparison between the simulations and observations we take the ratio
of the total mass of GC candidates in Auriga to the total GC mass in the MW 
(and M31). We use a diverging colour map centered around the overall median of the 
mass ratio (i.e. we subtract the median of these twenty-five bins from the value 
in each bin). We show this in the top (bottom) panel of Figure~\ref{fig:Au-FeHRgc-ratio}.
Note that the data in the three top right bins is masked because the mass ratio cannot 
be calculated due to zero mass in the observations (therefore the bins are white).
If the product of the bound cluster formation efficiency and consecutive GC 
disruption over a Hubble time would be constant, then the value in each bin would
have been zero. The red and blue bins indicate deviations from such as scenario and
indicate a higher and lower than average mass excess in the simulations. The median 
value used to shift the mass ratio is $2.68$ and $1.69$ dex for the MW and M31, 
respectively. This means that the median `mass budget' that the simulations `can 
afford to lose' is roughly a factor $480$ and $50$ for the MW and M31, respectively. 
The lowest mass surplus for both galaxies is the the bin where $-2.5 <$ [Fe/H] 
$< -1.5$ and $3 < r_{\text{gal}}/\text{kpc} < 8$, for which the simulations produce 
a factor $10^{2.68}/10^{1.33} \approx 22$ and $10^{1.69}/10^{0.75} \approx 9$ 
more mass in GC candidates than what is observed in the MW and M31 respectively.
The highest factor for the MW is $2.1 \times 10^{5}$, and $1.1 \times 10^{3}$
for M31.

>>>>

% Abstract of the paper
\begin{abstract}
We investigate whether the galaxy and star formation model used for the Auriga
simulations can produce a realistic GC population. We compare statistics of GC 
candidate star particles in the Auriga haloes with catalogues of the Milky Way 
(MW) and Andromeda (M31) GC populations. We find that the Auriga simulations do 
produce sufficient stellar mass for GC candidates at radii and metallicities that 
are typical for the MW GC system (GCS). We do observe varying mass-ratios of the
simulated GC candidates relative to the observed mass in the MW and M31 GC systems
for different bins of galactocentric radius-metallicity ($r_{\text{gal}}$-[Fe/H]).
This may imply that different values for the combined product of the bound cluster 
formation efficiency and the GC disruption rate are needed. Overall, the Auriga 
simulations produce GC candidates with higher metallicities than the MW and M31 
GCS and they are found at larger radii than observed. Bound cluster formation
efficiencies higher than ten percent are needed for the metal-poor GC candidates,
and those within the Solar radius should experience negligible destruction rates.
GC candidates in the outer halo, on the other hand, should either have low formation
efficiencies, or experience high mass loss for the Auriga simulations to produce a
GCS that is consistent with that of the MW or M31. Finally, the scatter in the 
metallicity as well as in the radial distribution between different Auriga runs 
is considerably smaller than the differences between that of the MW and M31 GCSs. 
The Auriga model is unlikely to give rise to a GCS that can be consistent with
both galaxies.
\end{abstract}

@@

This model was tailored to the \textsc{arepo} code and calibrated to reproduce
key observables of galaxies, such as the history of the cosmic star formation rate
density, the stellar mass to halo mass relation, and galaxy luminosity functions.
The galaxy formation model produces realistic spiral galaxies at redshift zero
that match observations such as sizes, morphologies (\citetalias{2017MNRAS.467..179G}),
HI disc properties \citep{2017MNRAS.466.3859M}, and the diversity of accreted stellar
halo properties \citep{2019MNRAS.485.2589M}. Furthermore, the simulations are able to
reproduce major Galactic components, such as the chemical thin/thick disc dichotomy
\citep{2018MNRAS.474.3629G} and the recently discovered \textit{Gaia} Sausage 
\citep{2019MNRAS.484.4471F}. They are thus a large set of detailed simulations
similar enough to the Galaxy to make predictions for the GC population properties
of the MW and M31.

@@

To ease this comparison between the simulations and observations we take the ratio
of the total mass of GC candidates in Auriga to the total GC mass in the MW 
(and M31). We use a diverging colour map centered around the overall median of the 
mass ratio (i.e. we subtract the median of these twenty-five bins from the value 
in each bin). We show this in the top (bottom) panel of Figure~\ref{fig:Au-FeHRgc-ratio}.
Note that the data in the three top right bins is masked because the mass ratio cannot 
be calculated due to zero mass in the observations (therefore the bins are white).
If the product of the bound cluster formation efficiency and consecutive GC 
disruption over a Hubble time would be constant, then the value in each bin would
have been zero. The red and blue bins indicate deviations from such a scenario and
indicate a higher and lower than average mass excess in the simulations. The median 
value used to shift the mass ratio is $2.68$ and $1.69$ dex for the MW and M31, 
respectively. This means that the median `mass budget' that the simulations `can 
afford to lose' is roughly a factor $480$ and $50$ for the MW and M31, respectively. 
The lowest mass surplus for both galaxies is the the bin where $-2.5 <$ [Fe/H] 
$< -1.5$ and $3 < r_{\text{gal}}/\text{kpc} < 8$, for which the simulations produce 
a factor $10^{2.68}/10^{1.33} \approx 22$ and $10^{1.69}/10^{0.75} \approx 9$ 
more mass in GC candidates than what is observed in the MW and M31 respectively.
The highest factor for the MW is $2.1 \times 10^{5}$, and $1.1 \times 10^{3}$
for M31.
